Market simulator

### 2020-09-19 analysis/05_market_simulator.Rmd
Running again, but broken

```{r load-data}
# Gammas of the "everything" model
gammas <- read_rds(
  here::here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')
  ) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i) %>% 
  t()

@@

Market Share
--------------------------------------

@@

  # Persona 2 expected utilities
  per2_org1_exp <- exp(t(org_choice[,3]) %*% as.matrix(per2_betas))
  per2_org2_exp <- exp(t(org_choice[,4]) %*% as.matrix(per2_betas))
  per2_org3_exp <- exp(t(org_choice[,5]) %*% as.matrix(per2_betas))
  per2_org3_exp <- exp(t(org_choice[,6]) %*% as.matrix(per2_betas))

@@

  # Organization name inputs
  org_reactive[,2] <- c(input$org1_id, input$org2_id, input$org3_id, input$org4_id)
  # Expected utilities and market shares
  org_reactive[,3] <- c(rep('Expected Utility', 4), rep('Market Share', 4))
  # Persona name inputs
  org_reactive[,4] <- c(rep(input$per1_id, 8), rep(input$per2_id, 8), rep(input$per3_id, 8))

@@

  ggplotly(
    org_reactive %>% 
      # Only care about the Market Share right now
      filter(Type == "Market Share") %>% 
      # Factor Organization and Persona with ordered=TRUE so the order doesn't change to alphabetical as names are created
      mutate(
        Organization = factor(
          Organization, 
          levels = c(input$org1_id, input$org2_id, input$org3_id, input$org4_id), 
          ordered = TRUE
        ),
        Persona = factor(
          Persona, 
          levels = c(input$per1_id, input$per2_id, input$per3_id), 
          ordered = TRUE
        )
      ) %>% 
      ggplot(aes(y = Value, x = Organization, fill = Persona)) +
      geom_bar(position = "dodge", stat = "identity") +
      labs(x="", y = "Market Share") + 
      scale_fill_manual(values = c("#FFC30B", "#28a153", "#c23838")) +
      theme(
        legend.position = "right",
        panel.background = element_blank(),
        panel.grid.major.y = element_line(color = "#D3D3D3")
      )
    )
})
```

Organizations and Personas {.tabset .tabset-fade}
--------------------------------------------------

@@

```{r org1-inputs}
# Naming
textInput(
  "org1_id",
  label = "Organization Name",
  value = "Organization 1",
  placeholder = "Enter Organization Name",
  width = "450px"
)

@@

```{r org2-inputs}
# Naming
textInput(
  "org2_id",
  label = "Organization Name",
  value = "Organization 2",
  placeholder = "Enter Organization Name",
  width = "450px"
)

@@

```{r org3-inputs}
# Naming
textInput(
  "org3_id",
  label = "Organization Name",
  value = "Organization 3",
  placeholder = "Enter Organization Name",
  width = "450px"
)

@@

```{r org4-inputs}
# Naming
textInput(
  "org4_id",
  label = "Organization Name",
  value = "Organization 4",
  placeholder = "Enter Organization Name",
  width = "450px"
)

@@

```{r per2-inputs}
# Naming
textInput(
  "per2_id",
  label = "Persona Name",
  value = "Persona 1",
  placeholder = "Enter Persona Name",
  width = "450px"
)

@@

```{r per3-inputs}
# Naming
textInput(
  "per3_id",
  label = "Persona Name",
  value = "Persona 1",
  placeholder = "Enter Persona Name",
  width = "450px"
)

>>>>

```{r load-data, message=FALSE}
# Gammas of the "everything" model
gammas <- read_rds(
  here::here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')
  ) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i) %>% 
  t()

@@

Market share
--------------------------------------

@@

  # Persona 2 expected utilities
  per2_org1_exp <- exp(t(org_choice[,3]) %*% as.matrix(per2_betas))
  per2_org2_exp <- exp(t(org_choice[,4]) %*% as.matrix(per2_betas))
  per2_org3_exp <- exp(t(org_choice[,5]) %*% as.matrix(per2_betas))
  per2_org4_exp <- exp(t(org_choice[,6]) %*% as.matrix(per2_betas))

@@

  # Organization name inputs
  org_reactive[,2] <- c(input$org1_name, input$org2_name, input$org3_name, input$org4_name)
  # Expected utilities and market shares
  org_reactive[,3] <- c(rep('Expected Utility', 4), rep('Market Share', 4))
  # Persona name inputs
  org_reactive[,4] <- c(rep(input$per1_id, 8), rep(input$per2_id, 8), rep(input$per3_id, 8))

@@

  ggplotly(
    org_reactive %>% 
      # Only care about the Market Share right now
      filter(Type == "Market Share") %>% 
      # Factor Organization and Persona with ordered=TRUE so the order doesn't change to alphabetical as names are created
      mutate(
        Organization = factor(
          Organization, 
          levels = c(input$org1_name, input$org2_name, input$org3_name, input$org4_name), 
          ordered = TRUE
        ),
        Persona = factor(
          Persona, 
          levels = c(input$per1_id, input$per2_id, input$per3_id), 
          ordered = TRUE
        )
      ) %>% 
      ggplot(aes(y = Value, x = Organization, fill = Persona)) +
      geom_bar(position = "dodge", stat = "identity") +
      labs(x="", y = "Market Share") + 
      scale_fill_manual(values = c("#FFC30B", "#28a153", "#c23838")) +
      theme(
        legend.position = "right",
        panel.background = element_blank(),
        panel.grid.major.y = element_line(color = "#D3D3D3")
      )
    )
})
```

Configurations {.tabset .tabset-fade}
--------------------------------------------------

@@

```{r org1-inputs}
# Naming
textInput(
  "org1_name",
  label = "Organization Name",
  value = "Organization 1",
  placeholder = "Enter Organization Name",
  width = "450px"
)

@@

```{r org2-inputs}
# Naming
textInput(
  "org2_name",
  label = "Organization Name",
  value = "Organization 2",
  placeholder = "Enter Organization Name",
  width = "450px"
)

@@

```{r org3-inputs}
# Naming
textInput(
  "org3_name",
  label = "Organization Name",
  value = "Organization 3",
  placeholder = "Enter Organization Name",
  width = "450px"
)

@@

```{r org4-inputs}
# Naming
textInput(
  "org4_name",
  label = "Organization Name",
  value = "Organization 4",
  placeholder = "Enter Organization Name",
  width = "450px"
)

@@

```{r per2-inputs}
# Naming
textInput(
  "per2_id",
  label = "Persona Name",
  value = "Persona 2",
  placeholder = "Enter Persona Name",
  width = "450px"
)

@@

```{r per3-inputs}
# Naming
textInput(
  "per3_id",
  label = "Persona Name",
  value = "Persona 3",
  placeholder = "Enter Persona Name",
  width = "450px"
)
